Structural replication of nanoporous media using procedural noise

### 2017-02-04 ms.tex
Small fixes at Hyttetur

Ideally, the model measure should pick up all geometrical properties that are relevant for the physical study of interest. For instance, pore size distribution and porosity are import for studying transport in porous media. Another such measure is the Distance-To-Atom (DTA). The method used for calculating porosity of a media is defined as in \cite{gelb1998characterization}, and we obtain the surface area of a porous media by using marching cubes triangulation to sum the surface area of the triangles.

In this paper, we choose to use the radial distribution function $g(r)$ as defined and implemented in LAMMPS \cite{plimpton1995fast}. The $g(r)$ (or pair correlation function) describes how density varies as a function of distance from a reference particle. Hereafter, $g_d(r)$ denotes the RDF calculated from simulated or experimental data, while $g_{M(\bar \theta)}(r)$ represents the RDF based on the procedural noise model $M(\bar \theta)$, where $\bar \theta$ are the set of model parameters.

@@

\subsection{Model verification: Parameter estimation of mock data}
\begin{figure}[htb!]
\includegraphics[width=.45\textwidth]{model_test.png}
\caption{Simulated mock data used for the initial model testing analysis. Input parameters are $\nu=0.03$,$\tau=-0.02$ and $\psi=0.6$.}
\label{fig:mockdata}
\end{figure}
In order to verify our likelihood code, we perform a model verification test on a mock data set with known input values. In this example, we only use standard simplex noise with three free parameters: the persistence $\psi$, threshold $\tau$ and scale $\nu$. We simulate a data set of $159 ^3 Å$ of $\sim 255 000$ atoms, and perform the cut-off given input parameters $\Omega=3$, $\Psi = 0.6$, $\tau=-0.2$, $\nu=0.03$. The resulting 3D structure is depicted in figure \ref{fig:mockdata}.

>>>>

Ideally, the model measure should pick up all geometrical properties that are relevant for the physical study of interest. For instance, pore size distribution and porosity are import for studying transport in porous media. In this paper, we choose to use the radial distribution function $g(r)$ as defined and implemented in LAMMPS \cite{plimpton1995fast}. The $g(r)$ (or pair correlation function) describes how density varies as a function of distance from a reference particle. Hereafter, $g_d(r)$ denotes the RDF calculated from simulated or experimental data, while $g_{M(\bar \theta)}(r)$ represents the RDF based on the procedural noise model $M(\bar \theta)$, where $\bar \theta$ are the set of model parameters.

The method used for calculating porosity of a media is defined as in \cite{gelb1998characterization}, and we obtain the surface area of a porous media by using marching cubes triangulation to sum the surface area of the triangles.

@@

\subsection{Model verification: Parameter estimation of mock data}
\begin{figure}[htb!]
\includegraphics[width=.45\textwidth]{model_test.png}
\caption{Simulated mock data used for the initial model testing analysis. Input parameters are $\nu=0.03$,$\tau=-0.02$ and $\psi=0.6$.}
\label{fig:mockdata}
\end{figure}
In order to verify our likelihood code, we perform a model verification test on a mock data set with known input values. In this example, we only use standard simplex noise with three free parameters: the persistence $\psi$, threshold $\tau$ and scale $\nu$. We simulate a data set of $159 ^3 \AA$ of $\sim 255 000$ atoms, and perform the cut-off given input parameters $\Omega=3$, $\Psi = 0.6$, $\tau=-0.2$, $\nu=0.03$. The resulting 3D structure is depicted in figure \ref{fig:mockdata}.
